\textbf{Atkins}: The Gantt chart below outlines my proposed work plan for successful completion of this project. The project will start on 1st August 2016 and I
plan to have submitted my final report by the 11th November 2016. This leaves one week as contingency for any unforeseen issues. The final due
date for submission is the 6th January 2016, so I am leaving myself flexibility if there are changes to the project scope through my work with
KYC.
As well as a kick-off meeting in the first week of the project, I will have four subsequent progress meetings with my supervisor over the length
of the project. 

\textbf{Dimmock}: Shows gantt chart

\textbf{Manchev}: This section outlines the work plan of the proposal as shown in Figure 3 and a Gantt chart is
displayed in Figure 4.
We have identified four milestones for the project. The first milestone is after the literature
view has been completed, the dataset selected, and the development platform (cloud instances)
established. The second milestone is reached after we have a working implementation of a
parallelized RBM with optimal network topology (number of nodes etc.) The next milestone
marks the end of the model training, after we have enough data to analyse the performance and
the impact of parallelization. The final milestone is reached on completion of the report.
The Gantt chart also includes 4 weeks of extra time for contingency, to reflect the mitigation
strategy outlined in the Risk Register (Table 1).

\textbf{Minah}: Shows WBS image and gantt chart

\textbf{Walters}: (Includes WBS and Gantt Chart). The work plan is shown in figure 1. The main tasks have been identified and split into sub
8
tasks. The project will start in April 2016 and finish in January 2017. If there is any time
deviation from the current plan this will be adapted to show this. If there is deviation above
reasonable bounds a new plan will be produced. Six weeks has been left for the write up
incorporating extra time incase any of the risks discussed occur.

\textbf{Wells}: Gantt chart, no text.