\textbf{TODO}: is this a section in its own right?  

\textbf{Atkins}: In developing this methodology, consideration was given to City University’s Research
Governance Framework. Importantly this project does not include any human participants.
After completing the University’s Ethics Review Form (see Appendix) and considering other
areas of potential legal and professional significance, no issues were identified for this
research.

\textbf{Dimmmock}: No text  

\textbf{Manchev}: The majority of this project involves technical work and statistical evaluation of computer
models carried out by the author. No other participants will be engaged and we foresee no
social, emotional, or physical discomfort being caused as a result of this work.
Certain concerns may be raised due to the requirements of available data for the training
process of Restricted Boltzmann Machines. For example, an RBM-based classifier used by a medical institution will require access to potentially sensitive and private patient information.
This issue has been studied in details by Li[31] and resolved by a suggested privacy-preserving
method for training Restricted Boltzmann Machines. However, all datasets considered in this
research will come from public repositories and working and storing private or sensitive data is
not anticipated.
All software that is required for conducting the research is released under copy-left licences
(Spark is licensed under Apache 2.0, LATEXis licensed under LPPL, R is licensed under GPLv3
etc.) Based on that we believe that there is no risk of breaching any copyright laws.
A Research Ethics check-list can be found at the end of the proposal.  

\textbf{Minah}: No text  

\textbf{Walters}: It must be ensured that all research is carried out without any chance of ethical, legal or
professional issues occurring. When reviewing the City University Ethics Review
Questionnaire there were no questions which required further action. Due to the nature of the
data provided from Opta a Non-Disclosure Agreement has been signed and must be upheld to
avoid any legal issues occurring.    


\textbf{wells}: This project does not involve people or any personally identifiable data. The performance tests will
be carried out on synthetic data rather than live data, and thus avoid any issues with confidentiality.

\textbf{Sikar}: Having completed \textit{Part A: Ethics Checklist} of the Research Ethics Review Form, as determined by the Computer Science Research Ethics Committee \cite{CSREC:2020}, we find that this proposed project work complies with research ethics guidelines and does not require ethical approval. 